Comparison of Confidence Interval in the OLS and Ridge Linear Regression Model: A Comparative study via Simulation

### 2024-10-03 draft_1.qmd

$$
CI width = \frac{\sum_{i=1}^{5000} (\hat{\beta}_U - \hat{\beta}_L)}{5000},
$$
$$
CP = \frac{\#(\hat{\beta}_L < \beta < \hat{\beta}_U)}{5000},
$$
All computations are performed with the R Statistical Software (v4.4.0; @r_soft).

***** explain something about the tables

# Results

>>>>

$$
CI width = \frac{\sum_{i=1}^{5000} (\hat{\beta}_U - \hat{\beta}_L)}{5000},
$$
$$
CP = \frac{\#(\hat{\beta}_L < \beta < \hat{\beta}_U)}{5000},
$$

A brief summary of the estimated MSE, coverage probability and width of the CI for sample size n = 30, 50, 100 and number of predictors, p = 3, 10 is presented in Table 1 - Table 6. All computations are performed with the R Statistical Software (v4.4.0; @r_soft).

# Simulation Results and Discussion

A shrinkage estimator is considered to perform better overall if the estimated MSE is comparatively lower than the OLS. When it comes to performance based on CIs, a shrinkage estimator that maintains the nominal coverage probability under various conditions but has a narrower CI width is more desirable. The key conclusions obtained from the tables based on these comparison criteria is explained below,

## Performance based on MSE

Plot 1: Performance based on MSE
![](mse_plot.jpeg)

## Performance based on Coverage Probability

Plot 2: Performance based on Coverage Probability
![](cp_plot.jpeg)
## Performance based on CI width

Plot 3: Performance based on CI width
![](ciw_plot.jpeg)

## Table 1: MSE results for n = 30, p = 3
## Table 2: Coverage Probability results for n = 30, p = 3
## Table 3: Confidence Interval width results for n = 30, p = 3
## Table 4: MSE results for n = 30, p = 10
## Table 5: Coverage Probability results for n = 30, p = 10
## Table 6: Confidence Interval width results for n = 30, p = 10

## Table 7: MSE results for n = 50, p = 3
## Table 8: Coverage Probability results for n = 50, p = 3
## Table 9: Confidence Interval width results for n = 50, p = 3
## Table 10: MSE results for n = 50, p = 10
## Table 11: Coverage Probability results for n = 50, p = 10
## Table 12: Confidence Interval width results for n = 50, p = 10

## Table 13: MSE results for n = 100, p = 3
## Table 14: Coverage Probability results for n = 100, p = 3
## Table 15: Confidence Interval width results for n = 100, p = 3
## Table 16: MSE results for n = 100, p = 10
## Table 17: Coverage Probability results for n = 100, p = 10
## Table 18: Confidence Interval width results for n = 100, p = 10
